\Huge \scshape \fontfamily{pbk}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \large An Example of the dndbook Class

### 2021-01-05 example.tex
Improvements to map index referencing, and better appendix formatting in table of contents

\title{The Dark \LaTeX{} \\
\large An Example of the dndbook Class}
\author{The rpgTeX Team}
\date{2020/04/21}

@@

\DndArea[\ref{map:The Kingdom}]{Mount Doofus}
This area has a prefix before the number. The prefix is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!

@@

>>>>

\title{
  \Huge \scshape \fontfamily{pbk}\selectfont
  The Dark \LaTeX{} \\
  \medskip
  \normalfont
  \large
  An Example of the dndbook Class
}
\author{The rpgTeX Team \and Steve}
\date{}

@@

\DndArea[The Kingdom]{Mount Doofus}
This area has a map reference before the number. The map name is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!

@@

\part{Appendices}

\appendix

\chapter{One Last Thing}

\DndDropCapLine{U}sing the |\appendix| command causes all subsequent chapters to be formatted as appendices. Neat!
